### 2008-12-06 doc/sec/Sec_paper.tex
changes including Aleks's comments, and other improvement

% This file was converted to LaTeX by Writer2LaTeX ver. 0.5
% see http://www.hj-gym.dk/~hj/writer2latex for more info
\documentclass{article}
\usepackage[ascii]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amsmath,amssymb,amsfonts,textcomp}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{pdftex, colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, pagecolor=blue, urlcolor=blue, pdftitle=, pdfauthor=qiangwz, pdfsubject=, pdfkeywords=}
\usepackage[pdftex]{graphicx}
% Text styles
\newcommand\textstyleStrongEmphasis[1]{\textbf{#1}}
\newcommand\textstyleCitation[1]{\textit{#1}}
% List styles
\newcommand\liststyleLi{%
\renewcommand\theenumi{\arabic{enumi}}
\renewcommand\theenumii{\arabic{enumii}}
\renewcommand\theenumiii{\arabic{enumiii}}
\renewcommand\theenumiv{\arabic{enumiv}}
\renewcommand\labelenumi{\theenumi.}
\renewcommand\labelenumii{\theenumii.}
\renewcommand\labelenumiii{\theenumiii.}
\renewcommand\labelenumiv{\theenumiv.}
}
\newcommand\liststyleLii{%
\renewcommand\labelitemi{${\bullet}$}
\renewcommand\labelitemii{${\circ}$}
\renewcommand\labelitemiii{${\blacksquare}$}
\renewcommand\labelitemiv{${\bullet}$}
}
\newcommand\liststyleLiii{%
\renewcommand\labelitemi{${\bullet}$}
\renewcommand\labelitemii{${\circ}$}
\renewcommand\labelitemiii{${\blacksquare}$}
\renewcommand\labelitemiv{${\bullet}$}
}
\newcommand\liststyleLiv{%
\renewcommand\theenumi{\arabic{enumi}}
\renewcommand\theenumii{\arabic{enumii}}
\renewcommand\theenumiii{\arabic{enumiii}}
\renewcommand\theenumiv{\arabic{enumiv}}
\renewcommand\labelenumi{\theenumi.}
\renewcommand\labelenumii{\theenumii.}
\renewcommand\labelenumiii{\theenumiii.}
\renewcommand\labelenumiv{\theenumiv.}
}
\newcommand\liststyleLv{%
\renewcommand\theenumi{\arabic{enumi}}
\renewcommand\theenumii{\arabic{enumii}}
\renewcommand\theenumiii{\arabic{enumiii}}
\renewcommand\theenumiv{\arabic{enumiv}}
\renewcommand\labelenumi{\theenumi.}
\renewcommand\labelenumii{\theenumii.}
\renewcommand\labelenumiii{\theenumiii.}
\renewcommand\labelenumiv{\theenumiv.}
}
% Page layout (geometry)
\setlength\paperwidth{8.5in}
\setlength\paperheight{11in}
\setlength\voffset{-1in}
\setlength\hoffset{-1in}
\setlength\topmargin{0.7874in}
\setlength\oddsidemargin{0.7874in}
\setlength\textheight{9.4251995in}
\setlength\textwidth{6.9251995in}
\setlength\footskip{0.0cm}
\setlength\headheight{0cm}
\setlength\headsep{0cm}
% Footnote rule
\setlength{\skip\footins}{0.0469in}
\renewcommand\footnoterule{\vspace*{-0.0071in}\setlength\leftskip{0pt}\setlength\rightskip{0pt plus 1fil}\noindent\textcolor{black}{\rule{0.25\columnwidth}{0.0071in}}\vspace*{0.0398in}}
% Pages styles
\makeatletter
\newcommand\ps@Standard{
  \renewcommand\@oddhead{}
  \renewcommand\@evenhead{}
  \renewcommand\@oddfoot{}
  \renewcommand\@evenfoot{}
  \renewcommand\thepage{\arabic{page}}
}
\makeatother
\pagestyle{Standard}
\title{}
\begin{document}
{\centering
Towards cross-middleware authentication and single sign-on for ARC grid
middleware
\par}

@@

\ \ \ \ In order to make the access to Grids as simple as possible,
security is one of the most important challenges in production Grids,
especially when the Grid applications are across multiple
administration domains as well as across heterogeneous Grid
middlewares, such as some wide scale eScience applications which needs
to coordinate resources sharing among collection of autonomous
institutions with different Grid middlewares running on these
resources. In this paper, we describe the security implementation and
consideration in new version of Advanced Resource Connector (ARC)
middleware, where the heterogeneity issue have been exploited. The main
goal of ARC implementation in terms of security is to let the
middleware be capable of interoperating with other Grid middlewares by
leveraging standard specifications. The key aspect of the work we have
done is to enhance the current proxy certificate based authentication
and single sign-on by utilizing and enhancing the standardized Web
Service specifications such as Security Assertion Markup Languages
(\textit{SAML}) single sign-on (SSO) profile, Web Services Security in
order to achieve cross-middleware authentication and single sign-on.

@@

\liststyleLi
\begin{enumerate}
\item[] {\centering
1. Introduction
\par}
\end{enumerate}
\ \ \ \ Grids provides the technology for wide-scale, cross domains
collaboration where the users work on resources and sharing data which
are distributed across domains. This kind of collaboration is called
virtual organization (VO)[1]. The resources that contribute to the VO
could come from independent administrative domains, and even require
different security approaches for control the access to themselves
because different middlerwares are used as platform. The same
heterogeneous situation even critically applies to users who need to
access the VO, because users holding one kind of credential could need
to travel through multiple resources with different security
approaches. To solve the above issues, the Grid middlewares should
provide the following ability: The user which participates the VO
should be able to access data and resources without being required to
constantly do authentication at each resource or data; The VO should be
able to easily manage the privileges or memberships to the users, and
VO together with its resources should be able to easily manage the
authorization, given the condition that the resources are owned by
different administrative domains.

\ \ \ \ In grid community, Grid Security Infrastructure (GSI)[2] is the
\textit{de facto} standard about authentication and \ transport level
communication, which builds on Public Key Infrastructure (PKI), an
architecture based on X.509 public key certificate. GSI implements some
enhancement (such as certificate delegation) based on standard SSL/TLS
protocol. Mutual authentication is required by GSI, and is the default
configuration for GSI based grid deployment; and X.509 certificates is
required for both of the client and service sides in order to achieve
mutual authentication. X.509 certificates is issued by trusted third
party called certificate authorities (CA), and then CAs constitute
trust federation and guarantee two different X.509 certificates from
different CAs can accomplish authentication to each other. So in the
GSI based grid system, if a user would access grid system, he/she
should own a X.509 certificate which is issued by a CA that is trusted
by other entity.

\ \ \ \ In terms of the virtual organization issues mentioned earlier,
GSI and some other related solutions like virtual organization
management service (VOMS) [3] have partly solved the them in some
sense. The identity delegation and X.509 proxy certificate initiated by
GSI can achieve single sign-on, so that the need to re-enter the
user{\textquotesingle}s pass phrase for authentication can be avoided
by creating the proxy certificate. \ As the most successful grid
authorization model, VOMS adopts Attribute Certificate[4]. Attribute
certificate is signed by VOMS server and then binded to proxy
certificates by client, \ and attributes certificate includes the VO
memberships which is associated with the proxy
certificate{\textquotesingle}s identity. Eventually the resources can
make access control decision based on parsing the VO membership
attributes from the homogeneous attribute certificate.

@@

\ \ \ Unfortunately, the existing grid security solutions such as GSI
and VOMS do not apply to Web Service \ based application very well due
to the following reasons:

\liststyleLii
\begin{itemize}
\item Firstly, \ the GSS API based confidential communication has also
not been adopted by Web Service implementation.
\item Secondly, \ Attribute Certificate has not been adopted by any Web
Service implementation at all.
\item Thirdly, Web Service implementations commonly use the Web Services
Security(WS-Security)[8], Security Assertion Markup Languages
(SAML)[9], and standard SSL/TLS as well as standard X.509 certificate
when considering security, which make them impossible to interoperate
with the GSI based grid middlewares.
\item Finally, identity delegation is a good solution for user or
user{\textquotesingle}s delegatee (on behalf of the user) to
move/travel from one resource to another resource. But since the
identity delegation has been completely coupled with the GSI
confidential communication process, it is not possible for the existing
identity delegation solution to be used by Web Service applications.
\end{itemize}
\ \ \ \ Moreover, the current grid security solutions require each user
to possess a X.509 certificate. But the process to get a certificate
may take quite long time, since the requester needs to be checked and
approved by the Registration Authority (RA) and then the Certificate
Authority (CA) can issue the certificate according to the approval from
RA. Meanwhile the process to use the certificate is also not so easy
for the wider less-IT focused research community to deal with, since
the user need to generate the proxy certificate by using the grid
specific command lines, such as \textit{grid-proxy-init}, and
\textit{voms-proxy-init}. On the other hand, users could most normally
have some local community/institutional credentials such as
username/passwords to which users are more familiar. To enable users to
use their own community credential instead of the X.509 certificate to
access grid is a promising solution to make the grid be more easily
accessible.

\ \ \ \ The above analysis shows that in order to achieve
interoperability and accessibility for user to access grid system which
is established on different middlewares, we need to address the
mismatch between the different security solutions from these
middlewares in order to ensure the interoperability as wide as
possible; also need to address the mismatch between
user{\textquotesingle}s normal experience and
middleware{\textquotesingle}s requirement in order to ensure the access
as simple as possible.

\ \ \ \ The approach in the new version of ARC is to utilize the
existing Web Service standards, such as SAML and WS-Security, to
achieve the interoperability and accessibility without breaking
existing grid specific security protocols.

\ \ \ \ The rest of this paper is organized as follows: Section 2 shows
the ARC grid middleware, especially the architecture of the new version
of ARC. Section 3 describes the consideration and implementation about
cross-middleware authentication and single sign-on is presented,
including a few solutions implemented for bridging the mismatch in
terms of authentication and single sign-on. Section 4 discusses the
related research, and Section 5 concludes.

@@

{\centering
2. ARC grid middleware 
\par}

\ \ \ \ ARC(Advanced Resource Connector) is an open source grid
middleware solution released under Apache license. ARC middleware
initially aimed at developing a grid middleware which provides
characteristics such as self-organized, fault-tolerant, non-intrusive,
easy-management [10]. \ Now \ the classic version of ARC provides grid
services such as grid job submission and management, resource
characterization, resource aggregation and discovery, basic data
management, integration of grid security solution, etc. Classic ARC has
been deployed and used in production environment, and been one of the
mainly deployed grid middlewares in Europe.

\ \ \ \ The new generation of ARC is based on the functionality and
capabilities of the classic ARC middleware, and it aims at implementing
a service-oriented middleware which will provide higher levels of
resource and user abstracting through well-defined web service
interface [11] in order to provide interoperability with other
service-based grid middlewares, as well as other Web Service compatible
applications.

\ \ \ \ As the key part of the implementation of new ARC middleware,
there is a lightweight Web Service container called Hosting Environment
Daemon (HED) which provides a host place for various services in
application level, as well as a host place for a bunch of modules to
support flexible, interoperatible, and efficient communication
mechanism for building SOAP based Web Services. The whole design of the
HED is built around the idea of flexibility and modularity, which means
for the developer, he can easily concentrate on the application level
Web Service implementation by only using the core minimum amount of
components if he only would do application level development, or he can
easily concentrate on the middleware level implementation such as
supporting another communication protocol or implementing
authentication mechanism by using the core minimum amount of components
and external dependencies; also for the deployer, he can easily
configure and deploy the middleware and application for different kinds
of requirements without being bothered to know much about the
implementation.

{\centering
Figure 1. The architecture of Host Environment Daemon
\par}

\begin{center}
\includegraphics[width=4.0673in,height=3.1047in]{Secpaper-img1.png}
\end{center}
\ \ \ \ The architecture of the HED is illustrated as Figure 1. In
general, there are a few \ components called Message Chain Component
(MCC) which are in charge of processing different messages for
different protocol levels. For instance, as shown in the example
message flow, HTTP MCC will process secure socket stream from TLS MCC
to generate output HTTP message to SOAP MCC, and also process SOAP
documentation from SOAP MCC to generate HTTP message to TLS MCC.

\ \ \ \ Two examples of MCC components configuration in Figure 1 shows
MCC are flexibly configurable: real line shows SOAP over HTTPS (HTTP
over TLS), while dotted line shows SOAP directly over TCP. Service
administrator can configure the MCCs according to the interoperability
requirement with the other part. For instance, the later example
configuration is compatible to WSE (Web Services Enhancement for .NET)
{\textquotesingle}s SOAP message mechanism (see WSE{\textquotesingle}s
\textit{SoapSender} and \textit{SoapReceiver}). Another configuration
could be SOAP over HTTPG (HTTP over GSI) which can be used to
interoperate with some service based on HTTPG such as Storage Resource
Manager (SRM)[12] \ service. The easily configurable characteristics
shows the flexibility of HED in terms of protocol supporting.

\ \ \ \ HED contains a framework for implementing and enforcing
authentication and authorization. Each MCC or Service has a common
interface for implementing various authentication and authorization
functionality. Each functionality can be implemented as a pluggable and
configurable component (plug-ins) called \textit{SecHandler} which is
C++ class and provides method for processing message that travels
through MCC or Service. Each MCC or Service is usually configured with
two queues of \textit{SecHandler} -- one for incoming message and one
for outgoing message respectively. All \textit{SecHandler} components
attached to the queue are executed sequentially. If any of them fails,
message processing fails as well. In Figure 1, the
{\textquotedblleft}AuthZ{\textquotedblright} and
{\textquotedblleft}AuthN{\textquotedblright} sub-module inside MCCs and
Services are examples of \textit{SecHandler}.

@@

\liststyleLiii
\begin{itemize}
\item \textit{Integration of community authentication} -{}-{}- to
utilize the standard-compatible community authentication mechanism from
Shibboleth [13] Identity Provider software when users authenticate
against Grid services.
\item \textit{Short lived credential service} \ {}-{}-{}- to issue the
short lived X.509 certificate for user by using the community
authentication, in order to interoperate with services that depends on
PKI based mutual authentication.
\item \textit{Credential delegation service} -{}-{}- to process the
X.509 credential delegation as a normal Web Service, in order to
provide single sign-on characteristic.
\item \textit{Message level authentication} -{}-{}- to provide message
level authentication by implementing WS-Security.
\item \textit{SAML token delegation service} -{}-{}- to process the WS
Security SAML token in order to provide single sign-on for SOAP message
level authentication.
\end{itemize}
3.1 Community based authentication for Grid by utilizing Shibboleth
Identity Provider

@@

\liststyleLiv
\begin{enumerate}
\item The client uses the user agent interface to launches a http
request including the IdP name (to which the user belongs) to the
service side. The endpoint of the SP service is the same as that of the
other target services, except the last part of the endpoint is
{\textquotedblleft}saml2sp{\textquotedblright} which is specific for
pointing to the SP Service. Note that we use Identity Provider (IdP)
name here to simplify the IdP discovery process in order to avoid the
IdP discovery process, because we suppose that user who would access
the target services should better know where is he from initially.
\item The SP Service (Service Provider) searches the metadata (we use
the same metadata format defined in Shibboleth) and gets the location
of the single sign-on service (hosted in IdP) and also the location of
assertion consuming service (hosted in this SP itself) in order to
compose the SAML {\textless}\textit{samlp:AuthnRequest}{\textgreater}
message. Then SP Service issues this
{\textless}\textit{samlp:AuthnRequest}{\textgreater} message by using
its own X.509 certificate (Note in the SAML SSO profile, certificate is
still needed by IdP and SP) and sends back to user agent.
\item User agent sends the
{\textless}\textit{samlp:AuthnRequest}{\textgreater} message to
Identity Provider.
\item Identity Provider requires an act of authentication. The
authentication mechanism is outside of the SAML2.0 SSO profile.
Shibboleth IdP implementation chooses some login handler for
authentication. The current user agent implementation is compatible to
\textit{Username/Password} login handler of Shibboleth IdP. Through the
http protocol, user agent will feed IdP with the username/password
which has been given by the caller of user agent interface.
\item Once the authentication has been succeeded, the IdP issues a SAML
response including an encrypted (encrypted by destination
SP{\textquotesingle}s public key) SAML assertion, and then this SAML
response will be delivered by the user agent to the Service Provider. 
\item The SP Service verifies and checks the SAML response, and decrypts
and stores the SAML assertion into session/connection context. The SAML
assertion includes the
{\textless}\textit{saml:AuthnStatement}{\textgreater} and
{\textless}\textit{saml:AttributeStatement}{\textgreater}.
\item The WS client launches the Grid/Web Service request via the same
connection as the one which is used by user agent to contact SP
Service.
\item The Grid/Web Service checks the
{\textless}\textit{saml:AuthnStatement}{\textgreater} from the session
context to see if the session is still valid through the
\textit{SecHandler} called {\textquotedblleft}\textit{SAML
SecHandler}{\textquotedblright}. If valid, service handles the service
processing and returns the response to WS client. Note that service
requires that WS client is from the same connection as the one on which
user agent contact SP service, in order to guarantee that the validity
of SSO profile result effects the WS client/Web Service interaction.
\end{enumerate}
\ \ \ \ The SP service and functional service(s) are hosted by the same
container, and they use the same X.509 credential. The client
authentication is switched off, so that client doesn{\textquotesingle}t
need to use any X.509 credential. Only the trusted certificates (CA
certificates for both SP and IdP) need to be configured for client side
so that SP and IdP can authenticate themselves to the client. As
required by SAML2.0 profile, the SP and IdP should have trust
relationship to each other.

@@

\ \ \ \ As shown in Figure 4, there is a specific WS client and Web
Service for processing delegation: delegation client, and delegation
service. The delegation service has two main \textit{WSDL}(Web Service
Description Language) operations, one for processing the delegation
initiation; the other for storing the signed proxy certificate. The
delegation process is detailed in Figure 5.

>>>>

% This file was converted to LaTeX by Writer2LaTeX ver. 0.5
% see http://www.hj-gym.dk/~hj/writer2latex for more info
\documentclass{article}
\usepackage[ascii]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amsmath,amssymb,amsfonts,textcomp}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{pdftex, colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, pagecolor=blue, urlcolor=blue, pdftitle=, pdfauthor=qiangwz, pdfsubject=, pdfkeywords=}
\usepackage[pdftex]{graphicx}
% Text styles
\newcommand\textstyleStrongEmphasis[1]{\textbf{#1}}
\newcommand\textstyleCitation[1]{\textit{#1}}
% List styles
\newcommand\liststyleLi{%
\renewcommand\theenumi{\arabic{enumi}}
\renewcommand\theenumii{\arabic{enumii}}
\renewcommand\theenumiii{\arabic{enumiii}}
\renewcommand\theenumiv{\arabic{enumiv}}
\renewcommand\labelenumi{\theenumi.}
\renewcommand\labelenumii{\theenumii.}
\renewcommand\labelenumiii{\theenumiii.}
\renewcommand\labelenumiv{\theenumiv.}
}
\newcommand\liststyleLii{%
\renewcommand\labelitemi{${\bullet}$}
\renewcommand\labelitemii{${\circ}$}
\renewcommand\labelitemiii{${\blacksquare}$}
\renewcommand\labelitemiv{${\bullet}$}
}
\newcommand\liststyleLiii{%
\renewcommand\labelitemi{${\bullet}$}
\renewcommand\labelitemii{${\circ}$}
\renewcommand\labelitemiii{${\blacksquare}$}
\renewcommand\labelitemiv{${\bullet}$}
}
\newcommand\liststyleLiv{%
\renewcommand\labelitemi{${\bullet}$}
\renewcommand\labelitemii{${\circ}$}
\renewcommand\labelitemiii{${\blacksquare}$}
\renewcommand\labelitemiv{${\bullet}$}
}
\newcommand\liststyleLv{%
\renewcommand\theenumi{\arabic{enumi}}
\renewcommand\theenumii{\arabic{enumii}}
\renewcommand\theenumiii{\arabic{enumiii}}
\renewcommand\theenumiv{\arabic{enumiv}}
\renewcommand\labelenumi{\theenumi.}
\renewcommand\labelenumii{\theenumii.}
\renewcommand\labelenumiii{\theenumiii.}
\renewcommand\labelenumiv{\theenumiv.}
}
\newcommand\liststyleLvi{%
\renewcommand\theenumi{\arabic{enumi}}
\renewcommand\theenumii{\arabic{enumii}}
\renewcommand\theenumiii{\arabic{enumiii}}
\renewcommand\theenumiv{\arabic{enumiv}}
\renewcommand\labelenumi{\theenumi.}
\renewcommand\labelenumii{\theenumii.}
\renewcommand\labelenumiii{\theenumiii.}
\renewcommand\labelenumiv{\theenumiv.}
}
% Page layout (geometry)
\setlength\paperwidth{8.5in}
\setlength\paperheight{11in}
\setlength\voffset{-1in}
\setlength\hoffset{-1in}
\setlength\topmargin{0.7874in}
\setlength\oddsidemargin{0.7874in}
\setlength\textheight{9.4251995in}
\setlength\textwidth{6.9251995in}
\setlength\footskip{0.0cm}
\setlength\headheight{0cm}
\setlength\headsep{0cm}
% Footnote rule
\setlength{\skip\footins}{0.0469in}
\renewcommand\footnoterule{\vspace*{-0.0071in}\setlength\leftskip{0pt}\setlength\rightskip{0pt plus 1fil}\noindent\textcolor{black}{\rule{0.25\columnwidth}{0.0071in}}\vspace*{0.0398in}}
% Pages styles
\makeatletter
\newcommand\ps@Standard{
  \renewcommand\@oddhead{}
  \renewcommand\@evenhead{}
  \renewcommand\@oddfoot{}
  \renewcommand\@evenfoot{}
  \renewcommand\thepage{\arabic{page}}
}
\makeatother
\pagestyle{Standard}
\title{}
\begin{document}
{\centering
Towards cross-middleware authentication and single sign-on for ARC grid
middleware
\par}

@@

\ \ \ \ In task of making the access to Grids as simple as possible,
security is one of the most important challenges in production Grid
infrastructures, especially when the Grid applications span across
multiple administration domains as well as across heterogeneous Grid
middlewares, such as some wide scale eScience applications which need
to coordinate resources sharing among collection of autonomous
institutions with different Grid middlewares running on these
resources. In this paper, we describe the security implementation and
consideration in new version of Advanced Resource Connector (ARC)
middleware, where the heterogeneity issue have been exploited. The main
goal of ARC implementation in terms of security is to let the
middleware be capable of interoperating with other Grid middlewares by
leveraging standard specifications. The key aspect of the work we have
done is to enhance the current proxy certificate based authentication
and single sign-on by utilizing and enhancing the standardized Web
Service specifications such as Security Assertion Markup Languages
(\textit{SAML}) single sign-on (SSO) profile, Web Services Security in
order to achieve cross-middleware authentication and single sign-on.

@@

\liststyleLi
\begin{enumerate}
\item[] {\centering
1. Introduction
\par}
\end{enumerate}
\ \ \ \ Grid provides the technology for wide-scale, cross domains
collaboration where the users work on resources and sharing data which
are distributed across domains. This kind of collaboration is called
virtual organization (VO)[1]. The resources that contribute to the VO
could come from independent administrative domains, and even require
different security approaches for control the access to themselves
because different middlerwares are used as platform. The same
heterogeneous situation applies to users who need to access the VO,
because users holding one kind of credential could need to travel
through multiple resources with different security approaches. To solve
the above issues, the Grid middlewares should provide the following
ability:

\liststyleLii
\begin{itemize}
\item The user which participates the VO should be able to access data
and resources without being required to constantly do authentication at
each resource or data; 
\item The VO should be able to easily manage the privileges or
memberships of the users; 
\item The VO together with its resources should be able to easily manage
the authorization, given the condition that the resources are owned by
different administrative domains.
\end{itemize}
\ \ \ \ In grid community, Grid Security Infrastructure (GSI)[2] is the
\textit{de facto} for authentication and \ transport level
communication, which builds on Public Key Infrastructure (PKI), an
architecture based on X.509 public key certificate. GSI implements some
enhancement (such as certificate delegation) based on standard SSL/TLS
protocol. Mutual authentication is required by GSI, and is the default
configuration for GSI based grid deployment. The X.509 certificates are
required for both the client and service sides in order to achieve
mutual authentication. The X.509 certificates are issued by trusted
third parties called certificate authorities (CA), and then CAs
constitute trust federation and guarantee two different X.509
certificates from different CAs can accomplish authentication to each
other. So in the GSI based Grid system, if a user would access Grid
system, he/she should own a X.509 certificate which is issued by a CA
that is trusted by other entity.

\ \ \ \ In terms of the virtual organization issues mentioned earlier,
GSI and some other related solutions like Virtual Organization
Management Service (VOMS) [3] have partly solved them in some sense.
The identity delegation and X.509 proxy certificate initiated by GSI
can achieve single sign-on, so that the need to re-enter the
user{\textquotesingle}s pass phrase for authentication can be avoided
by creating the proxy certificate. \ As the most successful Grid
authorization model, VOMS adopts Attribute Certificate[4] approach.
Attribute Certificate is signed by VOMS server and then binded to proxy
certificates by client, \ and attributes certificate includes the VO
memberships which is associated with the proxy
certificate{\textquotesingle}s identity. Eventually the resources can
make access control decision based on parsing the VO membership
attributes from the homogeneous attribute certificate.

@@

\ \ \ Unfortunately, the existing grid security solutions such as GSI
and VOMS do not apply to Web Service \ based applications very well due
to the following reasons:

\liststyleLiii
\begin{itemize}
\item The GSS API based confidential communication has also not been
adopted by Web Service implementation.
\item The Attribute Certificate has not been adopted by any Web Service
implementation at all.
\item Web Service implementations commonly use the Web Services
Security(WS-Security)[8], Security Assertion Markup Languages
(SAML)[9], and standard SSL/TLS as well as standard X.509 certificate
when considering security, which make them impossible to interoperate
with the GSI based grid middlewares.
\item Finally, identity delegation is a good solution for user or
user{\textquotesingle}s delegatee (on behalf of the user) to
move/travel from one resource to another resource. But since the
identity delegation has been completely coupled with the GSI
confidential communication process, it is not possible for the existing
identity delegation solution to be used by Web Service applications.
\end{itemize}
\ \ \ \ Moreover, the grid security solutions require each user to
possess a X.509 certificate. But the process to get a certificate may
take quite long time, since the requester needs to be checked and
approved by the Registration Authority (RA) and then the Certificate
Authority (CA) can issue the certificate according to the approval from
RA. Meanwhile the process to use the certificate is also not so easy
for the wider less-IT focused research community to deal with, since
the user need to generate the proxy certificate by using the grid
specific command lines, such as \textit{grid-proxy-init}, and
\textit{voms-proxy-init}. On the other hand, users could often have
some local community/institutional credentials such as
username/passwords to which users are more familiar. Enabling users to
use their own community credential instead of the X.509 certificate to
access grid is a promising solution to make the Grid more easily
accessible.

\ \ \ \ The above analysis shows that in order to achieve
interoperability and accessibility for user to access Grid system which
is established on different middlewares, we need to address the
mismatch between the different security solutions from these
middlewares in order to ensure the interoperability as wide as
possible; it is also necessary to address the mismatch between
users{\textquotesingle} usual experience and
middleware{\textquotesingle}s requirements in order to ensure the
access as simple as possible.

\ \ \ \ The approach in the new version of ARC is to utilize the
existing Web Service standards, such as SAML and WS-Security, to
achieve the interoperability and accessibility without breaking
existing Grid specific security protocols.

\ \ \ \ The rest of this paper is organized as follows: Section 2
presents the ARC Grid middleware, especially the architecture of the
new version of ARC. Section 3 describes the solution for
cross-middleware authentication and single sign-on, including
implementations for bridging the mismatch in terms of authentication
and single sign-on. Section 4 discusses the related research, and
Section 5 presents conclusion.

@@

{\centering
2. ARC Grid Middleware 
\par}

\ \ \ \ ARC(Advanced Resource Connector) is an open source Grid
middleware solution released under Apache license. ARC middleware
initially aimed at developing self-organized, fault-tolerant,
non-intrusive, easy-manageable Grid middleware [10]. \ Now \ the
classic version of ARC provides Grid services for job submission and
management, resource characterization, resource aggregation and
discovery, basic data management, integration of grid security
solution, etc. Classic ARC has been deployed and used in production
environment, and been one of the widely deployed Grid middlewares in
Europe.

\ \ \ \ The new generation of ARC is developed by KnowARC project [11],
based on the functionality and capabilities of the classic ARC
middleware. It aims at implementing a Web Service oriented middleware
which will provide higher levels of resource and user abstraction
through well-defined web service interface [12] in order to provide
interoperability with other service-based Grid middlewares, as well as
other Web Service compatible applications.

\ \ \ \ As the key part of the implementation of new ARC middleware,
there is a lightweight Web Service container called Hosting Environment
Daemon (HED) which provides a hosting for various services at
application level, as well as a bunch of modules to support flexible,
interoperatible, and efficient communication mechanism for building
SOAP based Web Services. The whole design of the HED is built around
the idea of flexibility and modularity, which means for the developer,
he can easily concentrate on the application level Web Service
implementation by only using the core minimum amount of components if
he only would do application level development, or he can work on the
middleware level implementing another communication protocol or
authentication mechanism by using the core minimum amount of components
and external dependencies; also for the deployer, he can easily
configure and deploy the middleware and application for different kinds
of requirements without being bothered to know much about the
implementation.

\begin{center}
\includegraphics[width=3.6362in,height=3.3339in]{Secpaper-img1.png}
\end{center}
{\centering
Figure 1. The example of Host Environment Daemon deployed with A-REX and
File services
\par}

\ \ \ \ The architecture of the HED is illustrated by Figure 1. In
general, there are few \ components called Message Chain Component
(MCC) which are in charge of implementing different protocol levels.
For instance, as shown in the example message flow, HTTP MCC will
process stream from TLS MCC to \ parse HTTP message and pass its body
to SOAP MCC, and also process SOAP response from SOAP MCC to generate
HTTP message for TLS MCC.

\ \ \ \ Dotted lines at Figure 1 show alternative path information can
propagate among MCCs. Service administrator can configure the MCCs
according to the interoperability requirements with the other part. For
instance, the configuration marked with dashed lines is compatible to
WSE (Web Services Enhancement for .NET) {\textquotesingle}s SOAP
message mechanism (see WSE{\textquotesingle}s \textit{SoapSender} and
\textit{SoapReceiver}). Another configuration could be SOAP over HTTPG
(HTTP over GSI) which is needed to interoperate with services like
Storage Resource Manager (SRM)[13] \ service. This shows the
flexibility of HED in terms of protocols support.

\ \ \ \ HED contains a framework for implementing and enforcing
authentication and authorization. Each MCC or Service has a common
interface for implementing various authentication and authorization
functionality. Each functionality can be implemented as a pluggable and
configurable component (plug-ins) called \textit{SecHandler} which is
C++ class and provides method for processing message that travels
through MCC or Service. Each MCC or Service is usually configured with
two queues of \textit{SecHandler} -- one for incoming message and one
for outgoing message respectively. All \textit{SecHandler} components
attached to the queue are executed sequentially. If any of them fails,
message processing fails as well. In Figure 1, the
{\textquotedblleft}AuthZ{\textquotedblright} and
{\textquotedblleft}AuthN{\textquotedblright} sub-modules inside MCCs
and Services are examples of \textit{SecHandler}.

@@

\liststyleLiv
\begin{itemize}
\item \textit{Integration of community authentication} -{}-{}- to
utilize the standard-compatible community authentication mechanism from
Shibboleth [14] Identity Provider software when users authenticate
against Grid services.
\item \textit{Short lived credential service} \ {}-{}-{}- to issue the
short lived X.509 certificates for users by using the community
authentication, in order to interoperate with services that depend on
PKI based mutual authentication.
\item \textit{Credential delegation service} -{}-{}- to process the
X.509 credential delegation as a normal Web Service, in order to
provide single sign-on characteristic.
\item \textit{Message level authentication} -{}-{}- to provide message
level authentication by implementing WS-Security.
\item \textit{SAML token delegation service} -{}-{}- to process the WS
Security SAML token in order to provide single sign-on for SOAP message
level authentication.
\end{itemize}
3.1 Community based authentication for Grid by utilizing Shibboleth
Identity Provider

@@

\liststyleLv
\begin{enumerate}
\item The client uses the user agent interface to launches a http
request including the IdP name (to which the user belongs) to the
service side. The endpoint of the SP service is the same as that of the
other target services, except the last part of the endpoint is
{\textquotedblleft}saml2sp{\textquotedblright} which is specific for
pointing to the SP Service. Note that we use Identity Provider (IdP)
name here to simplify the IdP discovery process in order to avoid the
IdP discovery process, because we suppose that user who would access
the target services should better know where is he from initially.
\item The SP Service (Service Provider) searches the metadata (we use
the same metadata format defined in Shibboleth) and gets the location
of the single sign-on service (hosted in IdP) and also the location of
assertion consuming service (hosted in this SP itself) in order to
compose the SAML {\textless}\textit{samlp:AuthnRequest}{\textgreater}
message. Then SP Service issues this
{\textless}\textit{samlp:AuthnRequest}{\textgreater} message by using
its own X.509 certificate (Note in the SAML SSO profile, certificate is
still needed by IdP and SP) and sends back to user agent.
\item User agent sends the
{\textless}\textit{samlp:AuthnRequest}{\textgreater} message to
Identity Provider.
\item Identity Provider requires an act of authentication. The
authentication mechanism is outside of the SAML2.0 SSO profile.
Shibboleth IdP implementation chooses some login handler for
authentication. The current user agent implementation is compatible to
\textit{Username/Password} login handler of Shibboleth IdP. Through the
http protocol, user agent will feed IdP with the username/password
which has been given by the caller of user agent interface.
\item Once the authentication has been succeeded, the IdP issues a SAML
response including an encrypted (encrypted by destination
SP{\textquotesingle}s public key) SAML assertion, and then this SAML
response will be delivered by the user agent to the Service Provider. 
\item The SP Service verifies and checks the SAML response, and decrypts
and stores the SAML assertion into session/connection context. The SAML
assertion includes the
{\textless}\textit{saml:AuthnStatement}{\textgreater} and
{\textless}\textit{saml:AttributeStatement}{\textgreater}.
\item The WS client launches the Grid/Web Service request via the same
connection as the one which is used by user agent to contact SP
Service.
\item The Grid/Web Service checks the
{\textless}\textit{saml:AuthnStatement}{\textgreater} from the session
context to see if the session is still valid through the
\textit{SecHandler} called {\textquotedblleft}\textit{SAML
SecHandler}{\textquotedblright}. If valid, service handles the service
processing and returns the response to WS client. Note that service
requires that WS client is from the same connection as the one on which
user agent contact SP service, in order to guarantee that the validity
of SSO profile result effects the WS client/Web Service interaction.
\end{enumerate}
\ \ \ \ The SP service and functional service(s) are hosted by the same
container, and they use the same X.509 credential. The client
authentication is switched off, so that client doesn{\textquotesingle}t
need to use any X.509 credential. Only the trusted certificates (CA
certificates for both SP and IdP) need to be configured for client side
so that SP and IdP can authenticate themselves to the client. As
required by SAML2.0 profile, the SP and IdP should have trust
relationship to each other.

@@

\ \ \ \ As shown in Figure 4, there is a specific WS client and Web
Service for processing delegation: delegation client, and delegation
service. The \textit{WSDL}(Web Service Description Language) of
delegation service has two main operations, one for processing the
delegation initiation, and \ the other for storing the signed proxy
certificate. The delegation process is detailed in Figure 5.
